### 2020-03-23 README.Rmd
run_cv with test fold buffer

scbi_cv_predict %>%
  inner_join(scbi_growth_df, by = 'focal_ID', suffix = c('_cv','')) %>%
  summarise(rmse_cv = sqrt(mean((growth - growth_hat_cv)^2)),
            rmse = sqrt(mean((growth - growth_hat)^2)) )

>>>>

scbi_cv_predict %>%
  inner_join(scbi_growth_df, by = 'focal_ID', suffix = c('_cv','')) %>%
  summarise(rmse_cv = sqrt(mean((growth - growth_hat_cv)^2)),
            rmse = sqrt(mean((growth - growth_hat)^2)), n() )
